Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-11 article.tex
Copied whole sections from the phd.tex.

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}

@@

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}

\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Theoretical Background}
\label{sec:back}
\vspace{-0.2cm}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
$1/({\rm m}\cdot{{\rm strad}})$) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein function,
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Image Acquisition Principle}
\label{sec:setup} \vspace{-0.2cm}

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
\begin{figure*}[t!]
  \begin{center}
    \vspace{-0.4cm}
    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
  \end{center}\vspace{-1.5cm}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}

Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,Martonchikc,vanMol}. However, current
multiview spaceborne systems are very coarse. For example, aerosol
retrieval in the most complex instrument, MISR, requires spatial
blocks that are about $17\times 17$km wide, each observed from just 9
views along-track. This practically leads to vertical radiative
transfer analysis, degenerating atmospheric analysis to
1D. Experimental airborne instruments under
development~\cite{baxter,dinerDavis10} may provide better, if still
coarse resolution once they are operational.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Forward Model}
\label{sec:skymodel} \vspace{-0.2cm}

This section describes models for image formation. In the consecutive
section, we describe how the image formation is inverted to recover
the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
Ground-based wide-angle sky-cameras capture the sky lightfield from
below. Per viewpoint, the view azimuth and elevation angles (relative
to the zenith and north) are encapsulated in the vector
${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
camera's location ${\bf x}$ is fixed, while any pixel in a frame
represents an angle ${\bf{\Theta}}$.  The measured radiance in all
locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
lightfield.
% Alternatively, several ground-based cameras can be mounted on moving
% vehicles, assuming that the aerosol distribution does not change
% much during the time-lapse of the camera trajectory.

Sunlight is scattered in the medium, creating {\em
  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
generally different, depending on the distribution of aerosols both
along a LOS, and along the SRs that hit the LOS.  As
Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
  x},{\bf{\Theta}}$) cut through different sets atmospheric
voxels. Thus, for each view, the radiance scattered from a voxel is
attenuated differently, depending on the distribution of aerosols
along the LOS~\cite{hansen}.

A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints. The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics. We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera. This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply. Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\

\vspace{-0.35cm}
\noindent
1. Attenuation of a SR propagating from the top of the atmosphere
(TOA) to voxel $k$. \\

\vspace{-0.35cm}
\noindent
2. Light scattering at voxel $k$, towards a camera.\\

\vspace{-0.35cm}
\noindent
3. Light attenuation on the LOS from voxel $k$ to the camera.

\noindent
Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
involves the scattering coefficient at voxel $k$, described in
Sec.~\ref{sec:scattering}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optical Depth}
\label{sec:optical-depth}

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
In addition, the infinitesimal volume contain also air
molecules. Hence, the overall extinction and scattering coefficients
in this small volume are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

@@

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
$q$. The geometric length of this intersection line segment is $\Delta
z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
  [0,1]$} expresses how much of the vertical thickness of $q$ is
crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
optical depth between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta(q)\Delta z  f_{\rm SR}(q)
  \;\;.
  \label{eq:lSRn}
\end{equation}
Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
\begin{equation}
  \tau_{\rm SR}(k)=
  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lSRaa}
\end{equation}
where
\begin{equation}
  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta^{\rm air}(q)  f_{\rm SR}(q)
  \label{eq:lSRair}
\end{equation}
and
\begin{equation}
  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
  \label{eq:lSRaeros}
\end{equation}

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
      & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
depths due to aerosols (See Fig.~\ref{fig:optidepth}):
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$. The overall
    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
    optical depth affecting $k$. It is formalized in matrix-vector
    operations. }
  \label{fig:optidepth}
\end{figure}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.

@@

\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}}

%
% subfiles is useful for having the abstract (and possible other
% sections/chapters) as separate files.
%
\usepackage{subfiles}

\usepackage[]{siunitx}

%
% The cleveref package seems very cool but currently it doesn't support hebrew
% (babel) very well, so I just use if for single references.
% As a work around I redefine the number definition as suggested in:
% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
%
\usepackage[capitalise]{cleveref}
\makeatletter
\def\@@number#1{#1}
\makeatother

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theoretical Background}
\label{sec:back}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units
\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
  extinction coefficient} $\beta$ (units \si{\per\meter}) is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
\cref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
\si[sticky-per]{\per\meter\steradian}) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein~\cite{Cornette1995} function\todo{Correct the Henyey-Greenstein function},
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model:
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Image Acquisition Principle}
\label{sec:setup}

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}
Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,Martonchikc,vanMol}. However, current
multiview spaceborne systems are very coarse. For example, aerosol
retrieval in the most complex instrument, MISR, requires spatial
blocks that are about $17\times 17$km wide, each observed from just 9
views along-track. This practically leads to vertical radiative
transfer analysis, degenerating atmospheric analysis to
1D. Experimental airborne instruments under
development~\cite{baxter,dinerDavis10} may provide better, if still
coarse resolution once they are operational.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Forward Model}
\label{sec:skymodel}

A forward model takes as input the aerosol distribution, and outputs
images as if captured at various viewpoints.  We use a
\emph{single-scattering} model, in which any SR changes direction
(scatters) only once on the way to the camera. This model is valid in
atmospheres that are not very dense: inside fog and clouds this model
does not apply.

Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bf{\Theta}}$.  A raw image is $i_{\bf
  x}({\bf{\Theta}})$: a camera's location ${\bf x}$ is fixed, while
any pixel in a frame represents an angle ${\bf{\Theta}}$.  The
measured radiance in all locations ${\bf x}$ and angles
${\bf{\Theta}}$ is the {\em lightfield} $I({\bf
  x},{\bf{\Theta}})$. Individual images are slices of the lightfield.

Under single-scattering approximation, radiative transfer has three
steps (\cref{fig:groundgrid}):
\begin{enumerate}
\item Attenuation of a SR propagating from the top of the atmosphere
  (TOA) to voxel $k$.
\item Light scattering at voxel $k$, towards a camera.
\item Light attenuation on the LOS from voxel $k$ to the camera.
\end{enumerate}

Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in \cref{sec:optical-depth}.  Step 2 involves
the scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Optical Depth}
\label{sec:optical-depth}

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
The infinitesimal volume contain also air molecules. Hence, the
overall extinction and scattering coefficients in this small volume
are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

@@

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
$q$. The geometric length of this intersection line segment is $l_{\rm
  SR}(q)$ which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.
Following \cref{eq:tau,eq:betair}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
Based on \cref{eq:betaer,eq:betair,eq:lSRn},
\begin{equation}
  \tau_{\rm SR}(k)=
  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lSRaa}
\end{equation}
where
\begin{equation}
  \tau_{\rm SR}^{\rm air}(k)=
  \sum_{q \in[{\rm SR},k]}
  \beta^{\rm air}(q)  l_{\rm SR}(q)
  \label{eq:lSRair}
\end{equation}
and
\begin{equation}
  \tau_{\rm SR}^{\rm aerosol}(k)
  \sum_{q \in[{\rm SR},k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm SR}(q)
  \label{eq:lSRaeros}
\end{equation}

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
\cref{eq:lSRaeros,eq:Dsv} lead to a vector of SR optical depths due to
aerosols (See \cref{fig:projection})a:
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. Similarly, \cref{eq:lSRair} leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $l_{\rm LOS_c}(q)$which
depends on $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:lSRaa,eq:lSRair,eq:lSRaeros}, the optical depth along a LOS
to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  l_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k) = \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm LOS_c}(q).
\end{align}
\cref{eq:lLOSaeros} leads to a vector of LOS optical depths due to
aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm LOS_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, \cref{eq:lSRair} leads to a vector of LOS optical depths
due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bf D}_c=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in all voxels, the
vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus $\vect{\tau}_c^{\rm
  air}$ can be calculated once, per sun zenith angle.

Using
\cref{eq:lSRaa,eq:tauSRvec1,eq:lLOSair,eq:tauLOSvec1,eq:Dtotal,eq:tauairtotal},
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
(See~\cref{fig:projection}a).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Scattering}
\label{sec:scattering}

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
which is pre-calculated.  Column-stacking all voxels yields the vector
representation of all scattering angles in the domain,
$\vect{\Phi}^{\rm scatter}_c$ per camera $c$. Similarly, the
single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are
stacked to vector $\vect{\varpi}$.  Using
\cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the angular
scattering coefficients across the domain are expressed in vector form
by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c) \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bf g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Image Capture}
\label{sec:captured-image}
